---
title: "2020 United States Federal Election Prediction: Joe Biden vs Donald Trump"
subtitle: "Application of multilevel regression with post-stratification (MRP) with "
author: "Xi Cheng, Guangyu Du, Shichao Feng and Zhitong Liu"
thanks: "Code and data are available at: https://github.com/Chelsea-Cheng99/STA304/tree/master/ProbSet4"
date: "October 31, 2020"
abstract: |
  | First sentence. Second sentence. Third sentence. Fourth sentence. 
  |
  | **Keywords:** forecasting;
output:
  bookdown::pdf_document2:
header_includes: 
   - \usepackage{amsmath} 
   - \usepackage{dcolumn}
toc: FALSE
bibliography: references.bib
---


```{r setup, include=FALSE, cache = FALSE}
# knitr settings
require("knitr")
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
opts_chunk$set(engine = "R")
knitr::opts_chunk$set(echo = T)
knitr::opts_chunk$set(message = F)
knitr::opts_chunk$set(warning = F)
## setting wd in DELL
# opts_knit$set(root.dir = "~/Documents/")
                                                 
## cache = F, if cache = T, will not revaluate code chunk everytime
## double or more space to insert a line break
```


```{r libs, echo = FALSE, warning= F}
######################
## Set up workspace
######################
# rm(list = ls())
# load required packages
require(tidyverse)
require(captioner)
require(stargazer)
require(lme4)

# require(magrittr)
# require(forcats)

options(stringsAsFactors = F)
options(dplyr.width = Inf)
# getwd()

# ######## clean memory ######################
# rm(list = ls())
# gc()
# is(dds)
# slotNames(dds)
```



# Introduction




# Data

Our data is of penguins (Figure \@ref(fig:bills)).

```{r bills, fig.cap="Bills of penguins", echo = FALSE}
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

Also bills and their average (Figure \@ref(fig:billssssss)). (Notice how you can change the height and width so they don't take the whole page?)

```{r billssssss, fig.cap="More bills of penguins", echo = FALSE, fig.width=8, fig.height=4}

# This needs to be about the random data tha tI sasmpled?
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk way more about it. 



# Model

\begin{equation}
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}  (\#eq:bayes)
\end{equation}

Equation \@ref(eq:bayes) seems useful, eh?


All work were done in `R` (version 4.0.2) [@R-base] and `Rstudio` (version 1.3.1093). `Tidyverse` (version 1.3.0) was used for data wrangling and visualization [@Tidyverse]. R package `forcats` (version 0.5.0) was also used for data pre-processing [@forcats].

# Results

# Discussion

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

# Appendix {-}

\newpage


# References


